\Large \bf Frontrunning

### 2018-08-06 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes

\subsection{Historical Context}
Frontrunning was first appeared on the Chicago Board Options Exchange (CBoE) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg CBoE) and SEC to regulate, detect and define laws and regulations to deal with frontrunning~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote}

As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, CBoE and other exchanges (and brokers) issued educational circulars for their members asserting that frontrunning violates existing rules, with some examples of what is considered frontrunning. However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.

@@

Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunnning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{finra_2012, sec2012frontrunning}.

@@

>>>>

\subsection{Historical Context}
Frontrunning was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and regulations to deal with frontrunning~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBoE).}
\end{quote}

As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that frontrunning violates existing rules, with some examples of what is considered frontrunning. However difference of opinion regarding the unfairness o front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.

@@

Initially the frontrunning policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the frontrunning rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{finra_2012, sec2012frontrunning}.

@@

% TODO: example with figure! similar to a traditional exchange. e.g an order on a decentral exchange, just the description then refer to \subsection{Financial Markets}
